Regression models for Cylindrical data in Psychology

### 2019-02-02 Manuscript/Manuscript.Rmd
R-code update

keywords          : "cylindrical data, regression, interpersonal behavior"
wordcount         : "X"

@@

#kable(PLSL, "latex", booktabs = T, escape = FALSE,
#      caption = "PLSL criteria, cross-validation mean and standard deviation, for the circular and linear outcome in the four cylindrical models")%>%
#add_header_above(c("Model" = 1, "Circular" = 2, "Linear" = 2))

@@

\caption{\label{tab:ModelFit}PLSL criteria, cross-validation mean and standard deviation, for the circular and linear outcome in the four cylindrical models}
\centering
\begin{tabular}[t]{lrlrl}
\toprule
\multicolumn{1}{c}{Model} & \multicolumn{2}{c}{Circular} & \multicolumn{2}{c}{Linear} \\
\cmidrule(l{2pt}r{2pt}){1-1} \cmidrule(l{2pt}r{2pt}){2-3} \cmidrule(l{2pt}r{2pt}){4-5}
  & mean & sd & mean & sd\\
\midrule
CL-PN & 82.96 & (9.47) & -17.65 & (3.70)\\
CL-GPN & 86.05 & (16.63) & -18.30 & (3.00)\\
Abe-Ley & 31.97 & (22.07) & 25.49 & (17.46)\\
GPN-SSN & 107.10 & (10.52) & -2.37 & (7.01)\\
\bottomrule
\end{tabular}
\end{table}

>>>>

keywords          : "cylindrical data, regression, interpersonal behavior"
#wordcount         : "X"

@@

#kable(PLSL, "latex", booktabs = T, escape = FALSE,
#      caption = "PLSL criteria, cross-validation mean and standard deviation, for the circular and linear outcome in #the four cylindrical models")%>%
#add_header_above(c("Model" = 1, "Circular" = 2, "Linear" = 2))

@@

\caption{\label{tab:ModelFit}PLSL criteria, cross-validation mean and standard deviation, for the circular and linear outcome in the four cylindrical models}
\centering
\begin{tabular}[t]{lrlrl}
\toprule
\multicolumn{1}{c}{Model} & \multicolumn{2}{c}{Circular} & \multicolumn{2}{c}{Linear} \\
\cmidrule(l{2pt}r{2pt}){1-1} \cmidrule(l{2pt}r{2pt}){2-3} \cmidrule(l{2pt}r{2pt}){4-5}
  & mean & sd & mean & sd\\
\midrule
CL-PN & 82.96 & (9.47) & -17.65 & (3.70)\\
CL-GPN & 78.21 & (14.53) & -18.30 & (3.00)\\
Abe-Ley & 31.97 & (22.07) & 25.49 & (17.46)\\
GPN-SSN & 107.10 & (10.52) & -2.37 & (7.01)\\
\bottomrule
\end{tabular}
\end{table}
